Q1 table

### 2021-11-04 Q1_table_characteristics_full.Rmd
update s1 table

@@

>>>>

#swap order, 3 and 4
fup4 <- Q1_table$fup___3
fup3 <- Q1_table$fup___4
Q1_table$fup___3 <- fup3
Q1_table$fup___4 <- fup4

@@

#change clusters to descriptions
Q1_table$study[Q1_table$study == "Harada S, 2020"] <- "Harada S, 2020 [Patients]"
Q1_table$study[Q1_table$study == "Harada S, 2020 [cluster 2]"] <- "Harada S, 2020 [Healthcare workers]"
Q1_table$study[Q1_table$study == "Kennelly SP, 2020"] <- "Kennelly SP, 2020 [Nursing home residents]"
Q1_table$study[Q1_table$study == "Kennelly SP, 2020 [cluster 2]"] <- "Kennelly SP, 2020 [Nursing home staff]"
Q1_table$study[Q1_table$study == "van Buul LW, 2020"] <- "van Buul LW, 2020 [Nursing home residents]"
Q1_table$study[Q1_table$study == "van Buul LW, 2020 [cluster 2]"] <- "van Buul LW, 2020 [Healthcare workers]"
Q1_table$study[Q1_table$study == "Theuring S, 2021"] <- "Theuring S, 2021 [School students and staff]"
Q1_table$study[Q1_table$study == "Theuring S, 2021 [cluster 2]"] <- "Theuring S, 2021 [Household members]"
Q1_table$study[Q1_table$study == "van den Besselaar JH, 2021"] <- "van den Besselaar JH, 2021 [Healthcare workers]"
Q1_table$study[Q1_table$study == "van den Besselaar JH, 2021 [cluster 2]"] <- "van den Besselaar JH, 2021 [Residents]"
Q1_table$study[Q1_table$study == "Taylor J, 2020"] <- "Taylor J, 2020 [Healthcare personnel]"
Q1_table$study[Q1_table$study == "Taylor J, 2020 [cluster 2]"] <- "Taylor J, 2020 [Residents]"
Q1_table$study[Q1_table$study == "Ladhani SN, 2020"] <- "Ladhani SN, 2020 [Residents]"
Q1_table$study[Q1_table$study == "Ladhani SN, 2020 [cluster 2]"] <- "Ladhani SN, 2020 [Healthcare workers]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:1]"] <- "#5551 Vohra [Presurgical patients]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:2]"] <- "#5551 Vohra [Undergoing chemotherapy]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:1]"] <- "#6526 Garibaldi [Residents]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:2]"] <- "#6526 Garibaldi [Staff]"
